YouTube Kids: The Effect of YouTube on Children’s Racial Learning

### 2025-04-14 d2mr_manuscript.qmd
old manuscript (d2mr)

---
title: "YouTube Kids: The Effect of YouTube on Children’s Racial Learning"
shorttitle: "YouTube Racial Attitudes"
author: 
- name: Reilly Amera
  corresponding: true
  email: ramera@uchicago.edu
  affiliations:
  - id: id1
    name: "University of Chicago"
    department: MA Program in the Social Sciences
    address: "1155 E 60th St."
    city: Chicago
    region: IL
    country: USA
    postal-code: 60637
abstract: "One way in which children learn about group dynamics within their racial world is from patterns in their daily environments. The current study seeks to understand the degree to which YouTube, a popular form of social media, exposes children to negatively valenced racial patterns, and potentially affects their beliefs. Dyads of parents and 8-13 year-old children (N = 18) describe daily YouTube usage, and the effects of children's YouTube usage are assessed. In the present sample, there is no relationship between children's YouTube usage, racial patterns they may observe, and negative racial beliefs."
floatsintext: true
numbered-lines: false
bibliography: [r-references.bib, bibliography.bib]
link-citations: true
draft-date: false
lang: en
language:
  citation-last-author-separator: "and"
  citation-masked-author: "Masked Citation"
  citation-masked-date: "n.d."
  citation-masked-title: "Masked Title"
  email: "Email"
format:
  apaquarto-html: default
  apaquarto-docx: default
  apaquarto-typst: 
    keep-typ: true
    list-of-figures: true
    list-of-tables: true
    toc: true
  apaquarto-pdf:
    documentmode: man
    keep-tex: true
    list-of-figures: true
    list-of-tables: true
editor: visual
---

@@

```{r}
#| label: fig-reg-v-mall
#| fig-cap: "Correlation Between Racial Regularities Score and Malleability Score"
#| fig-subcap: ["Full Sample", "Effects of daily use and participant race"]
#| layout-ncol: 2
#| fig-height: 6

>>>>

---
title: "YouTube Kids: The Effect of YouTube on Children’s Racial Learning"
shorttitle: "YouTube Racial Attitudes"
author: 
- name: Reilly Amera
  corresponding: true
  email: ramera@uchicago.edu
  affiliations:
  - id: id1
    name: "University of Chicago"
    department: MA Program in the Social Sciences
    address: "1155 E 60th St."
    city: Chicago
    region: IL
    country: USA
    postal-code: 60637
abstract: "One way in which children learn about group dynamics within their racial world is from patterns in their daily environments. The current study seeks to understand the degree to which YouTube, a popular form of social media, exposes children to negatively valenced racial patterns, and potentially affects their beliefs. Dyads of parents and 8-13 year-old children (N = 200 dyads) describe daily YouTube usage, and the effects of children's YouTube usage are assessed. In the present sample, there is no relationship between children's YouTube usage, racial patterns they may observe, and negative racial beliefs."
floatsintext: true
numbered-lines: false
bibliography: [r-references.bib, bibliography.bib]
link-citations: true
draft-date: false
lang: en
language:
  citation-last-author-separator: "and"
  citation-masked-author: "Masked Citation"
  citation-masked-date: "n.d."
  citation-masked-title: "Masked Title"
  email: "Email"
format:
  apaquarto-html: default
  apaquarto-docx: default
  apaquarto-typst: 
    keep-typ: true
    list-of-figures: true
    list-of-tables: true
    toc: true
  apaquarto-pdf:
    documentmode: man
    keep-tex: true
    list-of-figures: true
    list-of-tables: true
editor: visual
---

@@

```{r}
#| label: fig-reg-v-mall
#| fig-cap: "Correlation Between Racial Regularities Score and Malleability Score"
#| fig-subcap: ["Full Sample", "Effects of daily use and participant race"]
#| layout-ncol: 2
#| dfig-height: 6
